\LARGE \bf {\sc underworlds}: Cascading Situation Assessment for Robots

### 2018-02-26 paper.tex
Removed dependency on tikz that caused text formatting issues
Fixed missing ref

\documentclass[letterpaper, 10 pt, conference]{ieeeconf}

@@

\usepackage{tikz}
\usetikzlibrary{graphs,graphdrawing,arrows}
\usegdlibrary{trees, layered}
\usepackage{booktabs} % For formal tables
\usepackage{multicol}
\usepackage[bookmarks=true]{hyperref}

@@

\uwds is specifically inspired geometric and temporal reasoner like {\sc Spark}
(\emph{SPAtial Reasoning \& Knowledge})~\cite{sisbot2011situation}.  {\sc Spark}
acts as a situation assessment reasoner that generates symbolic knowledge from
the geometry of the environment with respect to relations between objects,
robots and humans. It also takes into account the different perspective that
each agent has on the environment. {\sc Spark} embeds a modality-independent
geometric model of the environment that serves both as basis for the fusion of
the perception modalities and as bridge with the symbolic
layer~\cite{lemaignan2016artificial}. This geometric model is built from 3D CAD
models of the objects, furniture and robots, and full body, rigged models of
humans. It is updated at run-time by the robot's sensors.  Likewise, \uwds
embeds a grounded amodal model of the environment, updated online from the
robot's sensors (sensor fusion).

However, {\sc Spark} is a monolithic module that does not support sharing its
internal 3D model with other external components. In contrast, \uwds focuses on
offering a shared and distributed representation of the environment within the
robot's software architecture. This also distinguishes \uwds from complex
cognitive toolkits like KnowRob (as found in OpenEASE~\ref{beetz2015open}).
While these tools maintain a spatio-temporal model of the world, this model is
internal and not meant to be made widely accessible to other external processes.
\uwds focuses instead on reusability and sharing of distributed spatio-temporal
models.  As such, \uwds can be seen as a middleware for spatio-temporal world
models and, contrary to KnowRob, it does \emph{not} provide any high-level
processing or reasoning capability (this is left to the users).

@@

\uwds provides an exemplary client ({\tt spatial\_relations}) to compute both
allo-centric and ego-centric (\ie viewer-dependent) spatial relations
between objects (Figure~\ref{fig|spatialrelations}).
Other libraries, like QSRLib~\ref{gatsoulis2016qsrlib}, that implement
computational models of Qualitative Spatial Relations could be trivially
combined with \uwds to provide more advanced geometric analysis.

@@

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{l2tor}
    \caption{TODO LAAS update archi -- Schema of the \uwds architecture used in
    the MuMMER project. }
    \label{fig|mummerarchitecture}
\end{figure}

The interaction scenario requires a number of \uwds clients. The clients are
distributed across...

>>>>

\documentclass[letterpaper, 10pt, conference]{ieeeconf}

@@

%\usepackage{tikz}
%\usetikzlibrary{graphs,graphdrawing,arrows}
%\usegdlibrary{trees, layered}
\usepackage[bookmarks=true]{hyperref}

@@

\uwds is specifically inspired by geometric and temporal reasoners like {\sc Spark}
(\emph{SPAtial Reasoning \& Knowledge})~\cite{sisbot2011situation}.  {\sc Spark}
acts as a situation assessment reasoner that generates symbolic knowledge from
the geometry of the environment with respect to relations between objects,
robots and humans. It also takes into account the different perspective that
each agent has on the environment. {\sc Spark} embeds a modality-independent
geometric model of the environment that serves both as basis for the fusion of
the perception modalities and as bridge with the symbolic
layer~\cite{lemaignan2016artificial}. This geometric model is built from 3D CAD
models of the objects, furniture and robots, and full body, rigged models of
humans. It is updated at run-time by the robot's sensors.  Likewise, \uwds
embeds a grounded amodal model of the environment, updated online from the
robot's sensors (sensor fusion).

However, {\sc Spark} is a monolithic module that does not support sharing its
internal 3D model with other external components. In contrast, \uwds focuses on
offering a shared and distributed representation of the environment within the
robot's software architecture. This also distinguishes \uwds from complex
cognitive toolkits like KnowRob (as found in OpenEASE~\cite{beetz2015open}).
While these tools maintain a spatio-temporal model of the world, this model is
internal and not meant to be made widely accessible to other external processes.
\uwds focuses instead on reusability and sharing of distributed spatio-temporal
models.  As such, \uwds can be seen as a middleware for spatio-temporal world
models and, contrary to KnowRob, it does \emph{not} provide any high-level
processing or reasoning capability (this is left to the users).

@@

\uwds provides an exemplary client ({\tt spatial\_relations}) to compute both
allo-centric and ego-centric (\ie viewer-dependent) spatial relations
between objects (Figure~\ref{fig|spatialrelations}).
Other libraries, like QSRLib~\cite{gatsoulis2016qsrlib}, that implement
computational models of Qualitative Spatial Relations could be trivially
combined with \uwds to provide more advanced geometric analysis.

@@

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{l2tor}
    \caption{TODO LAAS update archi -- Schema of the \uwds architecture used in
    the MuMMER project. }
    \label{fig|mummerarchitecture}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{laasudws}
    \caption{TODO LAAS update archi -- Schema of the \uwds architecture used in
    the MuMMER project. }
    \label{fig|mummerarchitecture}
\end{figure}
The interaction scenario requires a number of \uwds clients. The clients are
distributed across...
